Modelling BCG vaccination in the UK

### 2019-12-06 rmds/05-evidence-policy-change.Rmd
added minor sutherland corrections

Prior to the change in BCG vaccination policy in 2005 (see Chapter \@ref(background)) several studies were carried out to assess the impact of any potential policy change. In this Chapter I aimed to update one of these studies.

I recreated a previous approach for estimating the impact of ending the BCG schools scheme in England and Wales, updating the model with parameter uncertainty, and measurement error. I investigated scenarios considered by the Joint Committee on Vaccination and Immunisation (JCVI), and explored new approaches using notification data (see Chapter \@ref(data)). I estimated the number of vaccines needed to prevent a single notification, and the average annual additional notifications caused by ending the BCG schools’ scheme. This work was adapted from a preprint^[Preprint: https://doi.org/10.1101/624916] supervised by Hannah Christensen and Ellen Brooks-Pollock.

>>>>

Prior to the change in BCG vaccination policy in 2005 (see Chapter \@ref(background)) several studies were carried out to assess the impact of any potential policy change. In this Chapter, I aim to update one of these studies.

I will recreate a previous approach for estimating the impact of ending the BCG schools scheme in England and Wales, updating the model with parameter uncertainty, and measurement error. I investigate scenarios considered by the Joint Committee on Vaccination and Immunisation (JCVI), and explore new approaches using notification data (see Chapter \@ref(data)). I will estimate the number of vaccines needed to prevent a single notification, and the average annual additional notifications caused by ending the BCG schools’ scheme. This work was adapted from a preprint^[Preprint: https://doi.org/10.1101/624916] supervised by Hannah Christensen and Ellen Brooks-Pollock.
